Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-22 Docs/TODAES/paper.tex
paper new version: table and comments updated

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). \textcolor{red}{Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $XX$\% to ESBMC, $92$\% to $\nu$Z, and $YY$\% to ILP}. A time out condition (TO) is reached when the verification time is longer than $7200$ seconds. A memory out (MO) occurs when the tool reaches $24$GB of memory.

@@

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns two TOs (time-outs) related to Fuzzy and Mars benchmarks.

In contrast to ESBMC-$\nu$Z, ILP solves $6$ out of $7$ benchmarks. When ILP produces a result, it typically provides the optimal solution. On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z. On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.

Note further that all multi-core ESBMC implementations produce better results than the sequential one. In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase. One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $1$.$89$ times slower than ESBMC-$\nu$Z. However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools. When analyzing all benchmarks, ESBMC-PB produces TO or MO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.

@@

Note that RC$6$ produced time out for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced time-outs and memory-outs in all tools that aim to find the exact solution. ILP was the only one to solve Mars, while GA solved all benchmarks incorrectly.

The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO. ILP shows robustness and produces results even for a high number of nodes and edges.

@@

\bottomrule[1.5pt]
%ILP
\multirow{4}{*}{\textbf{\normalsize{ILP}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{2}   &  \normalsize{1}  &  \normalsize{2}   &  \normalsize{649}   &  \normalsize{1806}    &  \normalsize{TO}   &  \normalsize{5.42}  \\
&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  \normalsize{876}  \\
& & & & & & & & & \\
\hline

%GA
\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{7}   &  \normalsize{7}   &  \normalsize{9}   &  \normalsize{340}   &  \normalsize{2050}    &  \normalsize{1.37}   &  \normalsize{5000}  \\
&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0}   &  \normalsize{29}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  \normalsize{-27.5}  \\
& & & & & & & & & \\
\hline

%ESBMC
\multirow{4}{*}{\textbf{\normalsize{{ESBMC}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   & \normalsize{ 31}   &  \normalsize{362}   &  \normalsize{292}   &  \normalsize{3010}   & \normalsize{ TO}    &  \normalsize{MO}   &  \normalsize{MO } \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%MultiCore ESBMC
\multirow{4}{*}{\textbf{\normalsize{{ESBMC-SS}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   & \normalsize{ 2 }  &  \normalsize{6}   &  \normalsize{7 }  &  \normalsize{1615}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%ESBMC Parallel sequential
\multirow{4}{*}{\textbf{\normalsize{ESBMC-PS}}}
& & & & & & & & & \\
&  \normalsize{T(s)} &  \normalsize{4} &  \normalsize{10}   &  \normalsize{11}   &  \normalsize{2238}   &  \normalsize{TO}    &  \normalsize{MO}   &  \normalsize{MO}  \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%ESBMC Parallel Binary
\multirow{4}{*}{\textbf{\normalsize{{ESBMC-PB}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{6}   & \normalsize{ 5}   &  \normalsize{6}   &  \normalsize{207}   &  \normalsize{TO}    & \normalsize{MO}   & \normalsize{MO} \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

>>>>

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $15$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). \textcolor{red}{Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (pure, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA}. A time out condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory out (MO) occurs when the tool reaches $15$GB of memory.

@@

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (time-outs) related to RC6, Fuzzy and Mars benchmarks.

In contrast to ESBMC-$\nu$Z, ILP solves $5$ out of $7$ benchmarks. When ILP produces a result, it provides the optimal solution. On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z. On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.

Note further that all multi-core ESBMC implementations produce better results than the sequential one. In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase. One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $1$.$89$ times slower than ESBMC-$\nu$Z. However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools. When analyzing all benchmarks, ESBMC-PB produces TO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.

@@

Note that RC$6$ produced time out for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced time-outs and memory-outs in all tools that aim to find the exact solution. No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.

The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO. ILP shows robustness and produces results even for a high number of nodes and edges, but limited to $329$ nodes.

@@

\bottomrule[1.5pt]
%ILP
\multirow{4}{*}{\textbf{\normalsize{ILP}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{1.6}   &  \normalsize{1.3}  &  \normalsize{1.6}   &  \normalsize{648.9}   &  \normalsize{1806.2}    &  \normalsize{TO}   &  \normalsize{TO}  \\
&  \normalsize{Hp}   &  \normalsize{15}  &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  \normalsize{692}    &  -   &  -  \\
& & & & & & & & & \\
\hline

%GA
\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
& & & & & & & & & \\
\hline

%ESBMC
\multirow{4}{*}{\textbf{\normalsize{{ESBMC}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   & \normalsize{30.3}   &  \normalsize{313.7}   &  \normalsize{324.7}   &  \normalsize{MO}   & \normalsize{MO}    &  \normalsize{MO}   &  \normalsize{MO } \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  -   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%MultiCore ESBMC
\multirow{4}{*}{\textbf{\normalsize{{ESBMC-SS}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   & \normalsize{2.2}  &  \normalsize{5.8}   &  \normalsize{7.0}  &  \normalsize{1609.3}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31 }  &  \normalsize{241 }  &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%ESBMC Parallel sequential
\multirow{4}{*}{\textbf{\normalsize{ESBMC-PS}}}
& & & & & & & & & \\
&  \normalsize{T(s)} &  \normalsize{3.7} &  \normalsize{10.0}   &  \normalsize{12.0}   &  \normalsize{2468.0}   &  \normalsize{TO}    &  \normalsize{TO}   &  \normalsize{TO}  \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline

%ESBMC Parallel Binary
\multirow{4}{*}{\textbf{\normalsize{{ESBMC-PB}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{4.3}   & \normalsize{4.7}   &  \normalsize{6.3}   &  \normalsize{218.7}   &  \normalsize{TO}    & \normalsize{TO}   & \normalsize{TO} \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{38}   &  \normalsize{241}   &  -    &  -   &  -  \\
& & & & & & & & & \\
\hline
